The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-10 rational.tex
_

%\emph{Simultaneously} 
The execution begins at line~(0) with the value {{20}}. At line~(1)
values {{20}} and {{()}} flow forward, corresponding to the type
`{{a*1}}'. At line~(2) three independent subcomputations \emph{proceed
  concurrently}: the intial value {{20}} flowing from line (1) and two
entangled values, {{1/x}} and {{x}}, such that specifying one
implicitly specifies the dependant other. These three subcomputations
exist \emph{at the same time}. At line (3), the dependant {{1/x}} is
fixed to be the value {{20}}, thereby making fixing values of all
three branches.
%% the positive value created at line (2) which can flow to the
%% consumer; the negative value created at line (3) which can pay for the
%% debt created at line (2); and the initial value from line (0) which
%% can flow to the required forward-flowing value needed at line (3). 
At some intuitive level, one might understand the situation as
modeling a credit card payment in which money is created at line (2)
for the consumer together with a corresponding debt. The producer's
bank pays for the debt at line (3) and waits for the actual money to
arrive from the producer.

>>>>

%\emph{Simultaneously} 
The execution begins at line~(0) with the value {{20}}. At line~(1)
values {{20}} and {{()}} flow forward, corresponding to the type
`{{a*1}}'. At line~(2) three independent subcomputations \emph{proceed
  concurrently}: the intial value {{20}} flowing from line (1) and two
entangled values, let us call them {{1/x}} and {{x}}, such that
specifying one implicitly specifies the dependant other. These three
subcomputations exist \emph{at the same time}. At line (3), the
dependant {{1/x}} is fixed to be the value {{20}}, thereby making
fixing values of all three branches.
%% the positive value created at line (2) which can flow to the
%% consumer; the negative value created at line (3) which can pay for the
%% debt created at line (2); and the initial value from line (0) which
%% can flow to the required forward-flowing value needed at line (3). 
At some intuitive level, one might understand the situation as
modeling a credit card payment in which money is created at line (2)
for the consumer together with a corresponding debt. The producer's
bank pays for the debt at line (3) and waits for the actual money to
arrive from the producer.
